% -----------------------------------------------------------------
% Executive Summary
% -----------------------------------------------------------------
\sffamily
\Large
\noindent\textbf{Florida Bay Assessment Model Version 1.0 April 18, 2016}
\\[0.1in]
\noindent\textbf{User Manual}
\\[0.1in]
\normalsize
\noindent{HYDROLOGIC MODEL MANUAL}
\\[0.05in]
\noindent{SFNRC \reportnumber}
\\[0.1in]
\noindent\line(1,0){470}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{EXECUTIVE SUMMARY}
\rmfamily
\large

No estimate is more in danger of erroneous calculations\\
than those by which a man computes the force of his own genius.\\
\\-- Samuel Johnson

Since all models are wrong the scientist cannot obtain a "correct" one by excessive elaboration. On the contrary following William of Occam he should seek an economical description of natural phenomena. Just as the ability to devise simple but evocative models is the signature of the great scientist so overelaboration and overparameterization is often the mark of mediocrity.\\
\\-- George Box, \citep{Box1976}

The Florida Bay Assessment Model (BAM) is a simple basins hydrological model specific to Florida Bay.  The physical basis is exceedingly simple, conservation of mass, thereby the suggestion of Box may find some satisfaction.  Nonetheless, simplification and reductionism have dangers of their own, particularly when attempting to comprehend complexity as abounds in the natural world.

BAM attempts to balance the dimensional reduction of the physical description valued by Box with fidelity to the underlying complexities through use of the best available observational data describing the environment.  BAM leverages a rich set of high-fidelity observational data within Florida Bay administered by Everglades National Park: The Marine Monitoring Network, as well local tide predictions to address this need.  BAM is also unique in that it is pure Python.  Every aspect of the model is open, requiring no proprietary or special libraries or compilers.  The source code is object-oriented, designed to be readable and extensible, fostering community involvement and empowering the user to mold the model to suit their own understanding of the underlying processes. 

Dr. Johnson would no doubt question any claims of success and veracity regarding the usefulness of BAM, and as specifically observed by Box, the hope is that BAM will provide an economical description, albeit not a correct one, of natural phenomena in Florida Bay.

\cleardoublepage

